% \todo{RVWR1:
% P21, Section 7:  In modeling LPs by AIGs there is a restriction on simple normal LPs, and in modeling AIGs by LPs there is a restriction on AIGs with +head. There should be some remarks on these restrictions. E.g., Can they be removed? Or, why removing these restrictions create technical difficulties.}


%\todo{RVWR 2
%In this Section should appear a comparison/discussion with the connection with logic programming
%(in particular with the rewriting of sets of AICs in terms of logic programs) presented in
%(L. Caroprese, S. Greco, C. Sirangelo, E. Zumpano, Declarative Semantics of Production Rules
%for Integrity Maintenance. ICLP 2006) and
%(L. Caroprese, S. Greco, C. Molinaro, Prioritized Active Integrity Constraints for Database
%Maintanance. DASFAA 2007)
%}




% \subsection{AIC and Logic Programs}
\citet{tplp/CaropreseT11} defined a translation from logic programs to AICs as follows. 
\begin{definition}
  \label{defn:aic-transf}
 Let $r$ be a normal logic programming rule, 
 \[a\leftarrow \lit_1  \land \dots \land \lit_n.\]
 We define the active integrity constraint $\aicop (r)$ as 
 \[\lit_1\wedge\ldots\wedge\lit_n\wedge\neg a \aicrule \add a.\]
 Furthermore, if \PP is a normal logic program, we define 
 \[\aicop(\PP)=\bigcup\{\aicop(r)\mid r\in \PP\}.\]
\end{definition}

\citet{tplp/CaropreseT11} showed that \emph{for simple programs \PP}, an interpretation $I$ is a stable model of \PP if and only if $I$ (viewed as an update set) is a justified repair of $\langle\aicop(\PP),\emptyset\rangle$. Since $\aicop(\PP)$ is unipolar, from our earlier results (Propositions \ref{prop:stable_is_justified} and \ref{prop:justified_is_stable_sometimes}) it follows that this is also equivalent with the condition that $I$ is a $\threeap_{\aicop(\PP)}$-stable repair. 
The same result is also a corollary of the following stronger theorem. 
\begin{theorem}\label{thm:partialstable-LP}
 Let $\PP$ be a simple normal logic program and $\pstruct$ a partial interpretation. It holds that $\pstruct$ is a partial stable model of \PP if and only if $\pstruct$ is a partial stable repair of $\langle \aicop(\PP),\emptyset\rangle$. 
\end{theorem}
The proof of this theorem follows later, since it makes use of Theorem \ref{thm:lplink}. 
Since the well-founded model of a logic program is the least precise partial stable model, and an analogous relationship holds in the setting of AICs, we immediately find the following corollary. 

\begin{corollary}
 Let $\PP$ be a normal logic program. The well-founded model of \PP coincides with the AFT-well-founded repair of $\langle \aicop(\PP),\emptyset\rangle$. 
\end{corollary}

 While the operation $\aicop$ preserves (partial) stable, well-founded  fixpoints, it does not preserve grounded fixpoints or the Kripke-Kleene fixpoint (as the following two examples illustrate). In both cases, it is the intuition of \emph{inertia}, present in AICs but not in logic programs, that is responsible for the difference. 

 
\begin{example}\label{ex:grounded}
%   While the operation $\aicop$ preserves various types of AFT fixpoints, it does not preserve grounded fixpoint. 
  Consider the logic program 
  \[\PP_g = \left\{\begin{array}{ll}p&\lrule \lnot q\\ q&\lrule p \end{array} \right\}.\]
  Since $\mathcal{T}_{\PP_g}$ has no fixpoints, $\PP_g$ has no grounded models. 
  In this case, 
  \[\aicop(\PP_g) = \left\{\begin{array}{ll}\lnot p\land \lnot q &\aicrule \add p \\ p \land  \lnot q &\aicrule \add q\end{array}\right\}.\]
  Now, $\langle \aicop(\PP_g),\emptyset\rangle$ has one grounded repair, namely $\{\add p, \add q\}$. 
\end{example}
%% \bart{WAIT!!!! I'm getting confused here. 
%% In this example, isn't the AFT-well-founded repair $\{+p\}$, which is the nalso a stable repair? That would contradict Theorem \ref{thm:partialstable-LP} and also the combination of Propositions \ref{prop:stable_is_justified} and \ref{prop:justified_is_stable_sometimes}!

%% 7.2 surely is wrong. THe proof is simply bogus. $lp\circ aic \neq triv$ in general. Only if the logic program does not have the negation of its defined literal in the body. 

%% Also: the claim of Caroprese and Truzczynski ONLY holds for SIMPLE logic programs (Pg is NOT simple) . To be fixed!!!! 

%% }

\begin{example}
 Consider the logic program
 \[\PP_{kk}=\left\{ b\lrule a\right\}.\]
 The Kripke-Kleene model of this program maps both $a$ and $b$ to $\lfalse$. 
 The corresponding AIC 
 \[\aicop(\PP_{kk}) = \{\lnot b \land a \aicrule \add b\}\] 
 has a Kripke-Kleene repair that maps $a$ and $b$ to $\lunkn$, i.e., it is unknown if these need to be changed. 
\end{example}


It can be seen from the previous example that for AICs, the Kripke-Kleene semantics is very bad at deriving that something does \emph{not} need to be changed. The well-founded semantics is much stronger with that respect. 
In a certain sense, one might say that the intuition of ``inertia'' underlying AICs lies at the foundation of this discrepancy. 
Now, in logic programming, the Kripke-Kleene semantics exhibits similar behavior. Consider for instance the empty logic program 
\[ \PP_\emptyset = \{ \}.\]
This program has a Kripke-Kleene model in which each atom is false, as expected. 
However, adding a trivial rule
\[p\lrule p\]
 that ``simulates'' inertia results in a program with a Kripke-Kleene model in which $p$ is unknown.
 
 Inertia is also responsible for the discrepancy in Example \ref{ex:grounded}. 
 Intuitively, $\aicop(\PP_g)$ from that example corresponds more to the logic program
  \[\PP_g' = \left\{\begin{array}{l}p\lrule \lnot q \\ p\lrule p \\ q\lrule p\\ q\lrule q  \end{array}\right\}.\]
  Indeed $\aicop(\PP_g)$ states that if neither  $p$ nor $q$ are present in the database, add $p$, and once we add it, by inertia, it stays unless there is a reason to remove it again (which there is not), and similarly for $q$. 
  $\PP'$ and $\PP_g$ only differ from each other in the rules $p\lrule p$ and $q\lrule q$, which simulate inertia.
 
 
 The above discussion provides intuitions on what a transformation that preserves all AFT semantics should look like. In the following theorem, this is formalized. 

  


\begin{theorem}\label{thm:lplink}
  Suppose that $\db=\emptyset$ and that the only update actions in \aics are of the form $\add a$.
  The mapping $\actof$ induces an isomorphism between the lattices $2^\atoms$ and $2^\acts$ and between $(2^\atoms)^c$ and $(2^\acts)^c$. 
  Let $\lpop(\aics)$ denote the following logic program:  
 \begin{align*}
  \lpop(\aics)=& \{a \lrule \nup(r)\mid r\in \aics, \head(r)= \add a\}\\
  &\cup \{a \lrule a\mid a \in \atoms\}
 \end{align*}
 then for each partial interpretation \pstruct, $\Ap(\actof(\pstruct)) = \actof(\Psi_{\lpop(\aics)}(\pstruct))$. 
Hence, all AFT semantics for \fulldb coincide in this case with the equally-named semantics for the logic program $\lpop(\aics)$. 
\end{theorem}
%% \begin{proof}
%%   \luis{The complete proof has been done by hand. Should we add it, or is the detail given here enough?}
%%   \bart{I would add the complete proof, especially given the bug I discoverd recently, in a different Theorem... }
%%   By case analysis on the definition of \Ap.
%%   The condition on \fulldb guarantees that $\suppout$ is always false.
%%   The inclusion of the rules of the form $a\lrule a$ is necessary to mimic the common-sense law of inertia, which is embodied in the semantics for AICs but not in that of logic programs.
%% \end{proof}
\begin{proof}
  By definition,
  \begin{align*}
    \Psi_{\lpop(\aics)}(\pstruct)_1 &= \{a\in\atoms \mid \body(r)^\pstruct=\ltrue \mbox{ for some $r\in\lpop(\aics)$ with $\head(r)=a$}\} \\
    &= \{a\in\atoms \mid \nup(r)^\pstruct=\ltrue \mbox{ for some $r\in\aics$ with $\head(r)=+a$}\}\cup\{a\in\atoms\mid a^\pstruct=\ltrue\} \\
    &= \{\litof(\head(r)) \mid r\in\aics\land\nup(r)^\pstruct=\ltrue\}\cup\{a\in\atoms\mid a^\pstruct=\ltrue\}\\
    &= \{\litof(\alpha) \mid \supp_{\pstruct,\eta}(\alpha) = \ltrue \}\cup\{a\in\atoms\mid a^\pstruct=\ltrue\}
  \end{align*}
  Now, since, for each $\alpha \in \acts$, it holds that $\supp_{\pstruct,\eta}(\alpha^D) = \lfalse$ (since there are no rules with $\alpha^D$ in the head). 
  From the definition of \Ap, it then follows that
  \[ 
\Ap(\actof(\pstruct))_1 = \{\alpha \mid     \supp_{\pstruct,\eta}(\alpha) = \ltrue \text{ or } \alpha^{\actof(\pstruct)}=\ltrue\},
  \]
  i.e., that 
  \[\Ap(\actof(\pstruct))_1 =  \actof(\Psi_{\lpop(\aics)}(\pstruct)_1 ).\]
  
  Similarly, we also find that 
    \[\Ap(\actof(\pstruct))_2 =  \actof(\Psi_{\lpop(\aics)}(\pstruct)_2 )\]
    and the result follows. \qedhere
% 
\ignore{
  
  $\alpha\in \Ap(\actof(\pstruct))$ if and only if $\alpha \in \actof(\pstruct)$ or 
  Using, this, we see that: 
   \begin{align*}
    \Psi_{\lpop(\aics)}(\pstruct)_1 &= \{\litof(\alpha) \mid 
      \end{align*}

  \begin{align*}
    \Psi_{\lpop(\aics)}(\pstruct)_2 &= \{a\in\atoms \mid \body(r)^\pstruct\neq\lfalse \mbox{ for some $r\in\lpop(\aics)$ with $\head(r)=a$}\} \\
    &= \{a\in\atoms \mid \nup(r)^\pstruct\neq\lfalse \mbox{ for some $r\in\aics$ with $\head(r)=\add a$}\}\cup\{a\in\atoms\mid a^\pstruct\neq\lfalse\} \\
    &= \{\litof(\head(r)) \mid r\in\aics\land\nup(r)^\pstruct\neq\lfalse\}\cup\{a\in\atoms\mid a^\pstruct\neq\lfalse\}
  \end{align*}

  Note that (since $\db=\emptyset$), for each partial interpretation $\pstruct$, $\actof(\pstruct) (\db) = \pstruct$. 
  We proceed by case analysis on $a^\pstruct$.
  \begin{itemize}
  \item Assume $a^\pstruct=\ltrue$. In this case also $\actof(a)^{\actof(\pstruct)}=\ltrue$. Now, since $\aics$ cannot contain $\remove a$, we know that $\Ap(\actof(\pstruct))(\actof(a))=\ltrue=\Psi_{\lpop(\aics)}(\pstruct)(a)$.
  \item Assume $a^\pstruct=\lfalse$. In this case also $\actof(a)^{\actof(\pstruct)}=\lfalse$. Then 
  \[ \Ap(\actof(\pstruct))(\actof(a))=\supp_{\pstruct,\eta}(+a)=\max_{\leq_t}\{\nup(r)^{\pstruct}\mid r\in \aics \land \head(r) =\add a\}.\]
    If this last expression evaluates to $\ltrue$, then $a\in\Psi_{\lpop(\aics)}(\pstruct)_1$, and thus $\Psi_{\lpop(\aics)}(\pstruct)(a)=\ltrue$.
    If it evaluates to $\lunkn$, then $a\notin\Psi_{\lpop(\aics)}(\pstruct)_1$ but $a\in\Psi_{\lpop(\aics)}(\pstruct)_2$, hence $\Psi_{\lpop(\aics)}(\pstruct)(a)=\lunkn$.
    Finally, if it evaluates to $\lfalse$, then $a\notin\Psi_{\lpop(\aics)}(\pstruct)_2$, and hence $\Psi_{\lpop(\aics)}(\pstruct)(a)=\lfalse$.
    In all cases, we conclude that $\Ap(\pstruct)(a)=\Psi_{\lpop(\aics)}(\pstruct)(a)$.
  \item $a^\pstruct=\lunkn$: first observe that $\suppout_{\pstruct}(a)=\lfalse$, since $\remove a$ cannot be the head of any rule in $\aics$.
    Thus, if $\suppin_{\pstruct}(a)=\ltrue$, then $\Ap(\pstruct)(a)=\ltrue=\Psi_{\lpop(\aics)}(\pstruct)(a)$ by a reasoning similar to the previous case.
    Otherwise, necessarily $\Ap(\pstruct)(a)=\lunkn$, and again the previous reasoning establishes that $\Psi_{\lpop(\aics)}(\pstruct)(a)=\lunkn$.
    We again conclude that, in all cases, $\Ap(\pstruct)(a)=\Psi_{\lpop(\aics)}(\pstruct)(a)$.
  \end{itemize}
}
\end{proof}

%    \Psi_\PP(\pstruct)_1 &=\{a\in \voc\mid body(r)^\pstruct=\ltrue \text{ for some rule $r\in \PP$ with }head(r)=a\},\\
%    \Psi_\PP(\pstruct)_2 &=\{a\in \voc\mid body(r)^\pstruct\neq \lfalse \text{ for some rule $r\in \PP$ with }head(r)=a\}.


\begin{proof}[Proof of Theorem \ref{thm:partialstable-LP}]
 For each logic program \PP, let $\triv(\PP)$ denote the logic program 
 \[
  \triv(\PP) = \PP \cup \{p\lrule p\mid p\in \atoms\}.
 \]
 It is well-known\footnote{For completeness, we give the argument. Let $I$ be an interpretation; from the definition of partial stable fixpoint, it suffices to show that 
 $\lfp(\Psi_\PP(\cdot,I)_1)= \lfp(\Psi_{\triv(\PP)}(\cdot,I)_1)$ and that 
  $\lfp(\Psi_\PP(I,\cdot)_2)= \lfp(\Psi_{\triv(\PP)}(I,\cdot)_2)$. Since we are working with symmetric operators, it suffices to prove the first of the two equalities. 
  Now, it is easy to see that $\Psi_{\triv(\PP)}(\cdot,I)_1$ is the inflationary operator of $\Psi_\PP(\cdot,I)_1$, i.e., that $\Psi_{\triv(\PP)}(\cdot,I)_1(J) = \Psi_\PP(\cdot,I)_1(J)\cup J$. Hence, these two monotone operators have the same prefixpoints and thus also the same least prefixpoint, which equals their least prefixpoint. 
  }
 that the partial stable models of $\PP$ and those of $\triv(\PP)$ are the same. 
 Now, the result easily follows from the facts that \textbf{(i)} if $\PP$ is simple, then
\[
\lpop(\aicop(\PP)) = \triv(\PP)\]
since $\aicop$ adds a literal $\lnot a$ to the body of each rule $r$ with $\head(r) = a$ and $\lpop$ removes such literal again (since \PP is simple, there was no such literal at the start) and additionally, adds the trivial rules $\triv$ adds, and \textbf{(ii)} 
 that $\triv$ and $\lpop$ preserve partial stable models. 
% 
\end{proof}


\begin{example}\label{ex:unipolarno}
 Theorem \ref{thm:lplink} does not hold in general, not even for unipolar AICs. 
 Consider for instance the following sets of AICs. 
 \begin{align*}\eta_1 &= \left\{\begin{array}{l}
                    a \aicrule \remove a\\
                     b  \aicrule \remove b
                   \end{array}\right\}\\
                   \eta_2 &=\emptyset.
\end{align*}
These two are not equivalent under all AFT semantics. 
For the first one, the KK-repair is $\{\add a\mapsto\lfalse,\add b\mapsto\lfalse\}$, while for the latter, the KK-repair is $\{\add a\mapsto\lunkn,\add b\mapsto\lunkn\}$. However, they have the same translation to logic programs (since there are no rules with positive actions in the head).          
%                    
% 
\end{example}

The reason why the equivalence does not hold in the previous example is because rules with $\remove a$ in the head are ignored, while in the context of AICs such rules can make a semantic difference. 

\paragraph{Limitations and Related Work}
% \todo{Luis, can you give your opinion on this paragraph? I'm not so very convinced myself}
% \luis{I added a new 2nd paragraph}
In this Section, we studied mappings from sets of active integrity constraints to logic programs and back and how the semantics of the two formalisms relate. 
We briefly discuss the restrictions of this approach. 
In our translation of AICs to logic programs, namely in Theorem \ref{thm:lplink}, we assume that $\db=\emptyset$ and that the only update actions that occur in heads of rules are positive, i.e., of the form $\add a$. 
Since all our semantics satisfy the shifting property, the correspondence between the semantics still holds if \db is arbitrary but all actions in rule heads change \db. 
However, the condition that all actions in heads of rules change \db is essential,
%. We are not aware of a modular way to encode removal of atoms in the heads of logic programming rules. 
%Example \ref{ex:unipolarno} illustrates that this condition is indeed essential. 
as illustrated by Example~\ref{ex:unipolarno}.

The translation $\mathit{Rew}$ introduced by \citet{iclp/CaropreseGSZ06}, on the other hand, is at first sight more expressive than ours, as it applies to AICs with arbitrary actions on their head.
In order to deal also with removal actions (in the case of an empty database), the authors are required to consider a logic program with an extended signature that includes two copies of the database and two atoms for each possible update action.
They can then prove a precise correspondence between stable models of logic programs and founded repairs for AICs -- the only semantics that had been developed at that point in time. 
%to \cite{iclp/CaropreseGSZ06}.

However, their construction is very directly tailored to founded repairs, and it is not obvious that it can be adapted to AFT semantics.
In order to capture inertia, the authors duplicate all database atoms, so that every model contains both a copy of the original database and a copy of the repaired database.
Additional rules ensure that, in each model, the repaired database corresponds exactly to the result of applying the update actions also included in that model to the original database.
This technique does not enforce a correspondence of AFT semantics for AICs and for the corresponding logic program.
% It is easy to construct examples where e.g.~a grounded repair for a set of AICs does not correspond to a grounded model of the corresponding logic program because of the additional interpretations (for the logic program) where the set of update actions and the updated database do not match.
% \luis{I have such an example on paper, but including it implies defining their translation in detail, which I would rather avoid. What do you think?}
By contrast, the correspondence stated in Theorem~\ref{thm:lplink} holds for all different semantics considered in the current work.

Another limitation of our results is that for the reverse translation, we only preserve (partial) stable repairs and the AFT-well-founded repair (cfr Theorem \ref{thm:partialstable-LP}). 
However, our discussion does highlight where the difference comes from, namely the intuition of inertia. 
That is, as shown in the proof of Theorem \ref{thm:partialstable-LP}: for each simple normal logic program $\PP$, the semantics of $\triv(\PP)$ and $\aicop(\PP)$ coincide. 

Furthermore, we restrict our attention to \emph{normal} programs; \citet{tplp/CaropreseT11} discuss this translation without requiring normality. However, as mentioned before, we see non-normal AICs as syntactic sugar for their normalization and hence have no need for non-normal logic programs either. The same applies to the translation $\mathit{Rew}$ from~\citet{iclp/CaropreseGSZ06}.
The restriction that our programs are \emph{simple} is rather a technical requirement that simplifies proofs. For several semantics, this is non-essential: for (partial) stable and well-founded semantics, each program can easily be translated into an equivalent simple program.  


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../AFT-semantics-AIC.tex"
%%% End:
